### 2025-04-14 project1/nsSurvey.tex
21

To the best of our knowledge, Theorem~\ref{thm1:convergence-mse-prob} has not been explicitly stated in the literature.
It is the first result that shows the connections between the convergence in \gls{mse} and the convergence in probabilistic order for \gls{ae} in the context of nested simulation.
Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.

>>>>

Theorem~\ref{thm1:convergence-mse-prob} provides a formal connection between the \textcolor{red}{rate of convergence} in \gls{mse} and that in probabilistic order for \gls{ae} in the context of nested simulation.
It is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.

### 2025-04-14 project2/nnMetamodels.tex
21

Consider a generic \gls{va} contract with maturity $T>0$ periods, e.g., $T=240$ months.
Denote the policyholder's (random) time of death by $\tau>0$.
The contract expires at $T'=\min\{T,\tau\}$, which isthe earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be an indexed stock price, the subaccount value and a guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a \gls{va} contract affect the contract payout.
Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of \gls{va} such as \gls{gmab}, but this is not considered in our study for simplicity.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be a gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be a net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents incurred investment expenses.

@@

At any time $t=1,\ldots,T$, the insurer's liability in a \gls{va} contract is the present value of all payments, net of the fee income.
For example, suppose that the per-period risk-free rate is $r$, then
the insurer's time-$t$ liability for a \gls{gmmb} contract is $V_t = e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n$.
Also, the insurer's time-$t$ liability for a \gls{gmwb} contract is $V_t = \sum_{s=t+1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s] $.

For example, consider the time-$t$ liability $V_t$ of a \gls{gmwb}:
Suppose that given the stock sample path, which is an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $V_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
\begin{align}\label{eq2:delta}
    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial V_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\} \cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \nonumber \\
    t=0,\ldots,T-1,
\end{align}
where $\bm{1}\{\cdot\}$ is an indicator function and
\begin{align*}
    \frac{\partial \Ftilde_s}{ \partial S_t} &= \bm{1}\{\Itilde_{s-1} < \Ftilde_{s-1}\}\cdot\left( \frac{\partial \Ftilde_{s-1}}{ \partial S_t} - \frac{\partial \Itilde_{s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_s}{\Stilde_{s-1}}\cdot (1-\eta_g),\\
    \frac{\partial \Gtilde_s}{ \partial S_t} &= \bm{1}\{\Gtilde_{s-1} < \Ftilde_{s}\}\cdot\frac{\partial \Ftilde_{s}}{ \partial S_t} + \bm{1}\{\Gtilde_{s-1} \geq \Ftilde_{s}\}\cdot\frac{\partial \Gtilde_{s-1}}{ \partial S_t},\\
    \frac{\partial \Itilde_s}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_s}{ \partial S_t}.
\end{align*}
The recursion is initialized with $(\Stilde_t,\Ftilde_t,\Gtilde_t) = (S_t,F_t,G_t)$, $\frac{\partial \Ftilde_s}{ \partial S_t} = \frac{\Ftilde_t}{S_t}$, and $\frac{\partial \Gtilde_s}{ \partial S_t} = \frac{\partial \Itilde_s}{ \partial S_t} = 0$.

>>>>

Consider a generic \gls{va} contract with maturity $T>0$ periods, e.g., $T=240$ months.
Denote the policyholder's (random) time of death by $\tau>0$.
The contract expires at $T'=\min\{T,\tau\}$, which isthe earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be an indexed stock price, the subaccount value and a guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a \gls{va} contract affect the contract payout.
Let the triplet $X_t = (S_t, F_t, G_t)$ be the state of the \gls{va} contract at time $t$.
Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of \gls{va} such as \gls{gmab}, but this is not considered in our study for simplicity.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be a gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be a net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents incurred investment expenses.

@@

At any time $t=1,\ldots,T$, the insurer's liability in a \gls{va} contract is the present value of all payments, net of the fee income.
For example, suppose that the per-period risk-free rate is $r$, then
\textcolor{red}{the insurer's time-$t$ liability for a \gls{gmwb} contract is}

\begin{equation} \label{eq2:liability-gmwb}
    V_t = V(\mathbf{S}_t) = \mathbb{E} \left[ e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n \big\vert \mathbf{S}_t \right],
\end{equation}

where $\mathbf{S}_t = (S_0, S_1, \ldots, S_t)$ is the (outer) sample path up to time $t$, and the conditional expectation is taken with respect to the inner sample paths $\Stilde_{t+1},\ldots,\Stilde_{T}$ given the outer path $\mathbf{S}_t$.
The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
In practice, given the stock sample path, which is an outer path $S_1,\ldots,S_t$, one can simulate these future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$ with an inner simulation model that is based on some asset model such as \gls{gbm} or \gls{rsgbm}.
Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $V_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
\begin{align}\label{eq2:delta}
    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | \mathbf{S}_t) 
    & = \frac{\partial V_t}{\partial S_t} \nonumber \\
    & = \frac{\partial}{\partial S_t} \mathbb{E} \left[ e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n \big\vert \mathbf{S}_t \right] \nonumber \\
    & = \mathbb{E} \left[ \frac{\partial}{\partial S_t} \left( e^{-r(T-t)}\cdot (G_T - F_T)^+ - \sum_{s=t+1}^{T} e^{-r(T-s)} F_s \eta_n \right) \big\vert \mathbf{S}_t \right] 
\end{align}

For an inner simulation path $\Stilde_{t+1},\ldots,\Stilde_{T}$ of the \gls{gmwb} contract, the sensitivity of $V_t$ can be calculated by the following recursion:
\begin{equation}
    \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_{t,s} > \Ftilde_{t,s}\} \cdot \left( \frac{\partial \Itilde_{t,s}}{ \partial S_t} - \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right], \nonumber \\
    t=0,\ldots,T-1, 
\end{equation}
where $\bm{1}\{\cdot\}$ is an indicator function, $\Stilde_t = (S_{t, t+1},\ldots,S_{t, T})$, $\Ftilde_t = (F_{t, t+1},\ldots,F_{t, T})$, $\Gtilde_t = (G_{t, t+1},\ldots,G_{t, T})$, $\Itilde_t = (I_{t, t+1},\ldots,I_{t, T})$, and
\begin{align} \label{eq2:partial-derivatives}
    \frac{\partial \Ftilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Itilde_{t, s-1} < \Ftilde_{t, s-1}\}\cdot\left( \frac{\partial \Ftilde_{t, s-1}}{ \partial S_t} - \frac{\partial \Itilde_{t, s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_{t, s}}{\Stilde_{t, s-1}}\cdot (1-\eta_g),\nonumber \\
    \frac{\partial \Gtilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Gtilde_{t, s-1} < \Ftilde_{t, s}\}\cdot\frac{\partial \Ftilde_{t, s}}{ \partial S_t} + \bm{1}\{\Gtilde_{t, s-1} \geq \Ftilde_{t, s}\}\cdot\frac{\partial \Gtilde_{t, s-1}}{ \partial S_t},\nonumber \\
    \frac{\partial \Itilde_{t, s}}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_{t, s}}{ \partial S_t}.
\end{align}
At each inner simulation, the sample path at $t$ is initialized as:
\begin{equation}
    (\tilde{X}_{t, t}) = (\tilde{S}_{t, t}, \tilde{F}_{t, t}, \tilde{G}_{t, t}) = (S_t, F_t, G_t) = (X_t)
\end{equation}
W
Before withdrawal at $t$, the partial derivatives are initialized. $\tilde{F}_{t, t}$ is set to be proportional to $\tilde{S}_{t}$, such that:
\begin{equation}
    \frac{\partial \Ftilde_{t, t}}{ \partial S_t} = \frac{\partial F_t}{ \partial S_t} = \frac{F_t}{S_t}.
\end{equation}
$\tilde{G}_{t, t}$ and $\tilde{I}_{t, t}$ are fixed as constants, such that:
\begin{equation}
    \frac{\partial \Gtilde_{t, t}}{ \partial S_t} = \frac{\partial G_{t}}{ \partial S_t} = 0, \quad \frac{\partial \Itilde_{t, t}}{ \partial S_t} = \gamma \frac{\partial I_{t}}{ \partial S_t} = 0.
\end{equation}

Note that in \eqref{eq2:partial-derivatives}, no calculation is needed for $F_t < I_t$. 
In this case, the sub-account is already depleted at time $t$ and withdrawals are not allowed.
Therefore, \gls{gmwb}'s future liabilities beyond time $t$ are no longer affected by the stock price $S_t$, so no hedging is necessary.
In other words, when $F_t < I_t$, the inner simulation can be skipped and set $\Delta_t = 0$.
